Benchmarking on Rigetti architecture

### 2022-11-23 txt/maths.tex
Update maths.tex and direct_sum.tex

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
\usepackage{mathtools}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}

@@

\subsubsection{Quantum architecture's limits and practical solutions}

Let us take a closer look at the setup for distinguishing von Neumann 
measurements (see Fig.~\ref{fig:theoretical_scheme}). One of the components of 
this scheme is to perform a conditional  measurement. 
However, current NISQ devices do not allow for performing conditional 
 measurements.

We  will present two possible methods providing a clever way to cross this 
obstacle. These will be two schemes of practical realization. 
The first method consists in using postselection while the second method 
consists in applying a controlled unitary. These methods are described below.

\begin{scheme}(Postselection)

%\begin{figure}[h!]
%	\includegraphics[scale=1.5]{onequbit.pdf}
%	\caption{A schematic representation of the setup for distinguishing
%		measurements using postselection.}
%	\label{postselection}
%\end{figure}

\begin{enumerate}
\item We prepare  the discriminator $\ket{\psi_{0}}$ on bipartite system.
\item We perform one of two quantum channels, either $\Phi_{\Id}$ or 
$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left( \Phi \otimes \Id\right)(\proj{\psi_0})$.
\item We measure the first part of the input state  $\ket{\psi_{0}}$ and 
receive an output label $i$.
\item  
Based on Holevo--Helstrom theorem, we perform a conditional binary 
measurement	$\PP_{V_j}$ and hence, we implement the quantum channel $\Phi_{V_j^\dagger}$ on the second part. 
\item To calculate the probability of correct discrimination, we include just those cases for which $i = j$.
\item We measure the second part of the input state  $\ket{\psi_{0}}$ and make a
decision based on received label $j$. If $i=j=0$, then we decide that  
$\PP_U$ occurs.  If $i=j=1$, we decide that 
$\PP_{\Id}$ occurs.
\end{enumerate}

The schematic representation of this setup is depicted in 
Fig.~\ref{fig:postsellection}.

\begin{figure}[h!]
	\centering 
	\includegraphics[scale=1.7]{pics/postselection}

	\caption{ A schematic representation of the setup for distinguishing
		measurements using postselection. 
	}\label{fig:postsellection}
\end{figure}

Due to the fact that the measurement result is nondeterministic, we are forced to consider the following circuits
in the postselection procedure
\begin{equation}
\begin{split}
(\Phi_{U^\dagger}, \Phi_{V_k^\dagger}, i, j) \\ 
(\Phi_{\Id}, \Phi_{V_k^\dagger}, i, j)
\end{split}
\end{equation}
where $k=\{0,1\}, i=\{0,1\}$ and $ j=\{0,1\}$. 
The optimal probability $p_{\text{succ}}(\PP_{U}, \PP_{\Id}) $ of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is as follows
		\begin{equation}
		p_{\text{succ}}(\PP_{U}, \PP_{\Id})= \frac{\#(\Phi_{U^\dagger}, \Phi_{V_i^\dagger},i,0) + \#(\Phi_\Id, \Phi_{V_i^\dagger},i,1)}{\#(\Phi_{U^\dagger}, \Phi_{V_i^\dagger},i,j) + \#(\Phi_\Id, \Phi_{V_i^\dagger},i,j)}, 
		\end{equation}
where $i=\{0,1\}$ and $ j=\{0,1\}$.

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathtools}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}

@@

\subsubsection{Limitations of NISQ devices and practical discrimination schemes}

Current NISQ devices are unable to perform conditional measurements, which is the biggest
obstacle to implementing our scheme on real hardware. Luckily, we can overcome it by
cleverly adjusting our scheme so that it only uses components available on current devices.
We have two possible choices here: using a postselection or a direct sum
$V_0^\dagger\oplus V_1^\dagger$.

\begin{scheme}(By using postselection)

The first idea is very simple. Instead of performing a conditional measurement, for each
measurement $\PP_U, \PP_\Id$ to be discriminated and each choice of $k \in \{0, 1\}$ we run circuit presented in Fig. \ref{fig:postselection}.

\begin{figure}[h!]
	\centering
	\includegraphics[scale=1.7]{pics/postselection_no_channels}

	\caption{
		Postselection scheme of discrimination between von Neumann measurements $\PP_{U}$ and $\PP_\Id$.
	}\label{fig:postselection}
\end{figure}

But now our experiment does not match the previously described scheme, right?
Yes, unless we discard all the outcomes for which $i\ne k$ (hence the name \emph{postselection},
we are selecting valid outcomes after the experiment is performed).

% \begin{scheme}(Postselection)

% %\begin{figure}[h!]
% %	\includegraphics[scale=1.5]{onequbit.pdf}
% %	\caption{A schematic representation of the setup for distinguishing
% %		measurements using postselection.}
% %	\label{postselection}
% %\end{figure}

% \begin{enumerate}
% \item We prepare  the discriminator $\ket{\psi_{0}}$ on bipartite system.
% \item We perform one of two quantum channels, either $\Phi_{\Id}$ or
% $\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left( \Phi \otimes \Id\right)(\proj{\psi_0})$.
% \item We measure the first part of the input state  $\ket{\psi_{0}}$ and
% receive an output label $i$.
% \item
% Based on Holevo--Helstrom theorem, we perform a conditional binary
% measurement	$\PP_{V_j}$ and hence, we implement the quantum channel $\Phi_{V_j^\dagger}$ on the second part.
% \item To calculate the probability of correct discrimination, we include just those cases for which $i = j$.
% \item We measure the second part of the input state  $\ket{\psi_{0}}$ and make a
% decision based on received label $j$. If $i=j=0$, then we decide that
% $\PP_U$ occurs.  If $i=j=1$, we decide that
% $\PP_{\Id}$ occurs.
% \end{enumerate}

More precisely, our experiments can be grouped into classes identified by tuples of the form
$(\mathcal{Q}, k, i, j)$, where $\mathcal{Q} \in \{\PP_U, \PP_\Id\}$ denotes the chosen measurement.
We discard all the experiments for which $k \ne i$. Hence, the total number of valid experiments is

\begin{equation}
	N_\text{total} = \#\{(\QQ, k, i, j): k = i \}
\end{equation}

We now need to count the experiments (among the valid ones) resulting in successful discrimination.
If we have chosen $\PP_U$, then we guess correctly iff $j=0$. Similarly, for
$P_\Id$, we guess correctly iff $j=1$. If we define
\begin{eqnarray}
	N_{\PP_U} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_U, k = i, j = 0\} \\
	N_{\PP_\Id} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_\Id, k = i, j = 1\}
\end{eqnarray}
then the empirical success probability can be computed as

\begin{equation}
p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{N_{\PP_U} + N_{\PP_\Id}}{N_{\text{total}}}.
\end{equation}
